MSE and dynamic state variable model with sigma function

### 2018-10-24 doc/MSE_MAR_18.tex
fixed issues with citations

Our results suggest that in mixed fisheries, constraining quota for a single-species brought risk of eroding the production potential of unconstrained species when species differ only in spatial distribution. Both species in this study were the same with respect to growth, recruitment, mortality, and price, but differed in the location of their nursery habitat. The changes in production potential were caused by changing exploitation patterns in the fishery due to quota constraints in one species and the resulting spatial reallocation of fishing effort towards the nursery habitat of the other. The resulting change in age selectivity of the fishery decreased the production of the unmanaged stock (Fig. \ref{f:selectivity}).

@@

The forecasted effects of fisheries management in mixed fisheries result from individual choices by fishers on management and spatial heterogeneity in the resources rather than in differences in biological characestics of the resources. This emphsizes the need for incorporating detailed fishing dynamics. Histrocially, focus of management strategy evaluation has been primarily on managing the population (biological) dynamics of single and multispecies fisheries \cite{Butterworth1997, DelaMare1996, Dichmont2006, Punt1992, Punt1999, Punt2002, Smith1999}. Few MSE studies have explicitly incorporated the direct effects of human dimension harvesting on the stocks, although is equally important \cite{Fulton2011, Hilborn1985}. Human behaviour and decision-making are intrinsic parts of conservation and natural resource management. MSE with explicit human (social) behaviour dimension is increasingly being used \cite{Andersen2010, Ono2017} as fisheries science takes other sources of uncertainty to a greater extent to identify management actions that ensure the sustainability of fisheries.

@@

Finally, a dynamic state variable model was used as a tool to create a quick quota allocation and fleet dynamics model. Many detailed fleet dynamics models have been developed over the past decades \cite{Abbott2011, Ono2017, Simons2015} and they could have been used to include spatial factors as another dimension in the MSE. However, following \cite{Dowling2011}, incorporating uncertainty in errors in human dynamic decision-making help us to understant and predict changes in human behaviour in response of adopting a major policy change such as the CFP \cite{CFP2013}. The effect of introducing a realistic multispecies fishery within this MSE framework still remains the next step to be taken. Modelling and predicting realistic human behavior with its associated uncertainty in an ever-changing socioecological system will remain a major challenge to address in the future \cite{Ono2017}.

>>>>

Our results suggest that in mixed fisheries, constraining quota for a single-species can bring risk of eroding the production potential of unconstrained species when species differ only in spatial distribution. Both species in this study were the same with respect to growth, recruitment, mortality, and price, but differed in the location of their nursery habitat. The changes in production potential were caused by changing exploitation patterns in the fishery due to quota constraints in one species and the resulting spatial reallocation of fishing effort towards the nursery habitat of the other. The resulting change in age selectivity of the fishery decreased the production of the unmanaged stock (Fig. \ref{f:selectivity}).

@@

The forecasted effects of fisheries management in mixed fisheries result from individual choices by fishers on management and spatial heterogeneity in the resources rather than in differences in biological characestics of the resources. This emphsizes the need for incorporating detailed fishing dynamics. Histrocially, focus of management strategy evaluation has been primarily on managing the population (biological) dynamics of single and multispecies fisheries \cite{Butterworth2007, Dichmont2006b, Punt1999, Punt2009, Smith1999}. Few MSE studies have explicitly incorporated the direct effects of human dimension harvesting on the stocks, although is equally important \cite{Fulton2011}. Human behaviour and decision-making are intrinsic parts of conservation and natural resource management. MSE with explicit human (social) behaviour dimension is increasingly being used \cite{Andersen2010, Ono2018} as fisheries science takes other sources of uncertainty to a greater extent to identify management actions that ensure the sustainability of fisheries.

@@

Finally, a dynamic state variable model was used as a tool to create a quick quota allocation and fleet dynamics model. Many detailed fleet dynamics models have been developed over the past decades \cite{Andersen2010, Ono2018, Simons2015a} and they could have been used to include spatial factors as another dimension in the MSE. However, following \cite{Dowling2011}, incorporating uncertainty in errors in human dynamic decision-making help us to understant and predict changes in human behaviour in response of adopting a major policy change such as the CFP \cite{CFP2013}. The effect of introducing a realistic multispecies fishery within this MSE framework still remains the next step to be taken. Modelling and predicting realistic human behavior with its associated uncertainty in an ever-changing socioecological system will remain a major challenge to address in the future \cite{Ono2018}.
